---
documentclass: jss
author:
  - name: FirstName LastName
    affiliation: University/Company
    address: >
      First line
      Second line
    email: \email{name@company.com}
    url: http://rstudio.com
  - name: Second Author
    affiliation: Affiliation
title:
  formatted: "A Capitalized Title: Something about a Package \\pkg{foo}"
  # If you use tex in the formatted title, also supply version without
  plain: "A Capitalized Title: Something about a Package foo"
  # For running headers, if needed
  short: "\\pkg{foo}: A Capitalized Title"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [keywords, not capitalized, "\\proglang{Java}"]
  plain: [keywords, not capitalized, Java]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
---

# Introduction

This template demonstrates some of the basic latex you'll need to know to create a JSS article.

## Code formatting

Don't use markdown, instead use the more precise latex commands:

- \proglang{Java}
- \pkg{plyr}
- \code{print("abc")}

# R code

Can be inserted in regular R markdown blocks.

## MVN
```{r}
library(CuSMC)
mu = c(0, 0)
sigma = matrix(c(1, 0, 0, 1), nrow=2)
CuSMC::MVN(mu, sigma)
```

## MVNPDF
```{r}
library(CuSMC)
x = c(0, 0)
mu = c(0, 0)
sigma = matrix(c(1, 0, 0, 1), nrow=2)
CuSMC::MVNPDF(x, mu, sigma)
```

## MVT
```{r}
library(CuSMC)
mu = c(0, 0, 0)
sigma = diag(3)
nu = 3.0
CuSMC::MVT(mu, sigma, nu)
```

## MVTPDF
```{r}
library(CuSMC)
x = c(0, 0, 0)
mu = c(0, 0, 0)
sigma = diag(3)
nu = 3.0
CuSMC::MVTPDF(x, mu, sigma, nu)
```

## Metropolis-Hastings
```{r}
library(CuSMC)
N = 100
w = rnorm(N, 0, 1)
B = 10
CuSMC::metropolis_hastings(w, N, B)
```

## Installation
```{r, eval = FALSE}
install.packages("devtools")
install.packages("githubinstall")
```

## Installation 2
```{r, eval = FALSE}
library(devtools)
library(githubinstall)
githubinstall("CuSMC")
library(CuSMC)
```

## Installation 2
```{r, eval = FALSE}
library(devtools)
library(githubinstall)
githubinstall("CuSMC")
```